On Designing Collusion-Resistant Incentive Mechanisms for Mobile Crowdsensing Systems

### 2015-12-16 techreport.tex
Fix typos raised by Review 3.

Collusion attack is an important but difficult problem to address in general \cite{zhong2007designing, wang2006low, jurca2007collusion}. 
The difficulty lies in two aspects: \textbf{1)} A variety of collusion strategies (e.g., with or without profit trading) make the mitigation challenging. It means that in practice it requires security expertise to consider as many collusion scenarios as possible for a specific setting and provide technical solutions to mitigate the known collusion attacks. But like other penetration analysis, there is no guarantee of guard against unexamined cases. \textbf{2)} Difficulty exists when trying to provide theoretical guarantee of guard in the incentive mechanism design. 
As we mentioned earlier, since only strategyproofness cannot provide collusion resistance \cite{zhong2007designing}, people try to use other game theoretical solution concepts such as \emph{Group Strategyproof Equilibrium} \cite{jain1999group} to achieve collusion resistance. %So far  is one of the standard collusion resistant solutions that can give truthful mechanisms.
However, within the scope of wireless networks, sometimes it is not possible at all to achieve any group strategyproof equilibrium in some games. For example, one can never achieve any group strategyproofness in theory for noncooperative routing games in wireless ad hoc networks \cite{zhong2007designing}. When the possibility that colluding nodes can trade profit among them, this problem becomes even harder. For the same routing problem, we cannot obtain any strategyproofness if the colluding users can trade profit among them \cite{wang2006low}.

@@

\bolditem For another group of typical crowdsensing game, in which each contributing user finishes the assigned discrete sensing tasks to earn corresponding payment, we propose a concrete collusion-resistant incentive mechanism. %Sensing tasks are assigned by the crowdsensing platform based on the claimed cost of each user. 
%We propose an  to the discrete crowdsensing game. 
%(WE NEED TO EXPLAIN THE DIFFICULTY FOR DISCRETE MODEL, ESPECIALLY THE CHALLENGE WE FACE WHEN DEFENDING AGAINST PROFIT TRADING, WHICH IS DIFFERENT FROM CONTINUOUS MODEL.)
{\color{black}Differently from the case in which the sensing time can take any positive value, assigning discrete sensing tasks may let each user not have to be completely truthful, since usually a small perturbation on truthful strategy will not change the user utility. Hence it can be more difficult to establish a truthful incentive mechanism that can resist collusion, or even profit trading among the colluding nodes. 
However, we can show that our incentive mechanism can achieve group strategyproofness and t-truthfulness. In other words, our solution can defend against colluded cheating, even with profit trading.}

@@

{\color{black}
The major objective of designing incentive mechanisms is to achieve a equilibrium, the state when each user has maximized its own utility and no user can increase its utility by unilaterally taking a different strategy. If one expects to eliminate the possibility that some users take actions deceitfully, a \emph{strategyproof} equilibrium is required. %Strategyproof equilibrium satisfies Incentive Compatibility (IC) and Individual Rationality (IR). IC says each user has to make actions truthfully (i.e., to report its sensing cost honestly) to maximize its utility, and IR says each user utility must be non-negative since any user can quit the game to avoid negative utility. 
Unfortunately, a strategyproof equilibrium is not strong enough to eliminate collusion among the users, since it is possible that some users \emph{collude} to alter their strategies simultaneously, in order to let some of them gain more utilities without decreasing any utility of theirs \cite{zhong2007designing}.

@@

{\color{black}
\section{System Models and Problem Formulation}
\label{sec:PFSM}
{\color{black}
In this section, we formalize a popular type of crowdsensing scenarios, and then describe a typical strategyproof incentive mechanism. We also present an example to present how collusion attack can make this incentive mechanism fail. %At last we will discuss the assumptions of discrete crowdsensing game.
%We will also discuss the privacy preserving problem against traffic analysis and timing attacks.
}

>>>>

Collusion attack is an important but difficult problem to address in general \cite{zhong2007designing, wang2006low, jurca2007collusion}. 
The difficulty lies in two aspects: \textbf{1)} A variety of collusion strategies (e.g., with or without profit trading) make the mitigation challenging. It means that in practice it requires security expertise to consider as many collusion scenarios as possible for a specific setting and provide technical solutions to mitigate the known collusion attacks. But like other penetration analysis, there is no guarantee of guard against unexamined cases. \textbf{2)} Difficulty exists when trying to provide theoretical guarantee of guard in the incentive mechanism design. 
As we mentioned earlier, since only strategyproofness cannot provide collusion resistance \cite{zhong2007designing}, people try to use other game theoretical solution concepts such as \emph{Group Strategyproof Equilibrium} \cite{jain1999group} to achieve collusion resistance. %So far  is one of the standard collusion resistant solutions that can give truthful mechanisms.
However, within the scope of wireless networks, sometimes it is not possible at all to achieve any group strategyproof equilibrium in some games. For example, one can never achieve any group strategyproofness in theory for noncooperative routing games in wireless ad hoc networks \cite{zhong2007designing}. When it is possible that colluding nodes can trade profit among them, this problem becomes even harder. For the same routing problem, we cannot obtain any strategyproofness if the colluding users can trade profit among them \cite{wang2006low}.

@@

\bolditem For another group of typical crowdsensing games, in which each contributing user finishes the assigned discrete sensing tasks to earn corresponding payment, we propose a concrete collusion-resistant incentive mechanism. %Sensing tasks are assigned by the crowdsensing platform based on the claimed cost of each user. 
%We propose an  to the discrete crowdsensing game. 
%(WE NEED TO EXPLAIN THE DIFFICULTY FOR DISCRETE MODEL, ESPECIALLY THE CHALLENGE WE FACE WHEN DEFENDING AGAINST PROFIT TRADING, WHICH IS DIFFERENT FROM CONTINUOUS MODEL.)
{\color{black}Differently from the case in which the sensing time can take any positive value, assigning discrete sensing tasks may let each user not have to be completely truthful, since usually a small perturbation on truthful strategy will not change the user utility. Hence it can be more difficult to establish a truthful incentive mechanism that can resist collusion, or even profit trading among the colluding nodes. 
However, we can show that our incentive mechanism can achieve group strategyproofness and t-truthfulness. In other words, our solution can defend against colluded cheating, even with profit trading.}

@@

{\color{black}
The major objective of designing incentive mechanisms is to achieve an equilibrium, the state when each user has maximized its own utility and no user can increase its utility by unilaterally taking a different strategy. If one expects to eliminate the possibility that some users take actions deceitfully, a \emph{strategyproof} equilibrium is required. %Strategyproof equilibrium satisfies Incentive Compatibility (IC) and Individual Rationality (IR). IC says each user has to make actions truthfully (i.e., to report its sensing cost honestly) to maximize its utility, and IR says each user utility must be non-negative since any user can quit the game to avoid negative utility. 
Unfortunately, a strategyproof equilibrium is not strong enough to eliminate collusion among the users, since it is possible that some users \emph{collude} to alter their strategies simultaneously, in order to let some of them gain more utilities without decreasing any utility of theirs \cite{zhong2007designing}.

@@

{\color{black}
\section{System Models and Problem Formulation}
\label{sec:PFSM}
{\color{black}
In this section, we formalize a popular type of crowdsensing scenarios, and then describe a typical strategyproof incentive mechanism. We also present an example to illustrate how collusion attack can make this incentive mechanism fail. %At last we will discuss the assumptions of discrete crowdsensing game.
%We will also discuss the privacy preserving problem against traffic analysis and timing attacks.
}
